The Concurrent Calculi Formalisation Benchmark\thanks{The work is partially supported by EPSRC EP/T006544/2.}

### 2024-04-15 short-paper/short-paper.tex
change
ack added
Add a full stop to ack.
Rework research questions and design goals to be more concise..

\title{The Concurrent Calculi Formalisation Benchmark}

\author{
     Marco Carbone \inst{1}\orcidID{0000-0001-9479-2632}
\and David Castro-Perez \inst{2}\orcidID{0000-0002-6939-4189}
\and Francisco Ferreira \inst{3}\orcidID{0000-0001-8494-7696}
\and Lorenzo Gheri \inst{4}\orcidID{0000-0002-3191-7722}
\and Frederik Krogsdal Jacobsen \inst{5}\orcidID{0000-0003-3651-8314}
\and Alberto Momigliano \inst{6}\orcidID{0000-0003-0942-4777}
\and Luca Padovani \inst{7}\orcidID{0000-0001-9097-1297}
\and Alceste Scalas \inst{5}\orcidID{0000-0002-1153-6164}
\and Dawit Tirore \inst{1}\orcidID{0000-0002-1997-5161}
\and Martin Vassor \inst{8}\orcidID{0000-0002-2057-0495}
\and Nobuko Yoshida \inst{8}\orcidID{0000-0002-3925-8557}
\and Daniel Zackon \inst{9}\orcidID{0009-0008-6153-2955}
}

@@

Similarly to the authors of POPLMark, we seek to answer several questions:
\begin{enumerate}[label=\textbf{(Q\arabic*)},leftmargin=10mm]
\item\label[question]{item:rq1} What is the current state of the art in the mechanisation of  the meta-theory of process calculi?
\item\label[question]{item:rq2} Which techniques and best practices can be recommended when starting new mechanisation projects involving process calculi?
\item\label[question]{item:rq3} What improvements are needed to make mechanisation tools more user-friendly with regard to the issues faced when mechanising process calculi?
\end{enumerate}

@@

\item\label{item:goal-reusability} To prioritise the exploration of mechanisation
  techniques that are reusable for future research.
\end{enumerate}
We also aim at strengthening the culture of mechanisation, by rallying the community to collaborate on exploring and developing new tools and techniques.

>>>>

\title{The Concurrent Calculi Formalisation Benchmark\thanks{The work is partially supported by EPSRC EP/T006544/2.}}

\author{
     Marco Carbone \inst{1}\orcidID{0000-0001-9479-2632}
\and David Castro-Perez \inst{2}\orcidID{0000-0002-6939-4189}
\and Francisco Ferreira \inst{3}\orcidID{0000-0001-8494-7696}
\and Lorenzo Gheri \inst{4}\orcidID{0000-0002-3191-7722}
\and Frederik Krogsdal Jacobsen \inst{5}\orcidID{0000-0003-3651-8314}
\and Alberto Momigliano\thanks{Member of the Gruppo Nazionale Calcolo Scientifico-Istituto Nazionale di Alta Matematica (GNCS-INdAM).} \inst{6}\orcidID{0000-0003-0942-4777}
\and Luca Padovani \inst{7}\orcidID{0000-0001-9097-1297}
\and Alceste Scalas \inst{5}\orcidID{0000-0002-1153-6164}
\and Dawit Tirore \inst{1}\orcidID{0000-0002-1997-5161}
\and Martin Vassor \inst{8}\orcidID{0000-0002-2057-0495}
\and Nobuko Yoshida \inst{8}\orcidID{0000-0002-3925-8557}
\and Daniel Zackon \inst{9}\orcidID{0009-0008-6153-2955}
}

@@

Similarly to the authors of POPLMark, we seek to answer several questions about the mechanisation of the meta-theory of process calculi:
\begin{enumerate}[label=\textbf{(Q\arabic*)},leftmargin=10mm]
\item\label[question]{item:rq1} What is the current state of the art?
\item\label[question]{item:rq2} Which techniques and best practices can be recommended?
\item\label[question]{item:rq3} What improvements are needed to make mechanisation tools more user-friendly?
\end{enumerate}

@@

\item\label{item:goal-reusability} To prioritise the exploration of reusable mechanisation techniques.
\end{enumerate}
We also aim at strengthening the culture of mechanisation, by rallying the community to collaborate on exploring and developing new tools and techniques.
